---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

#title: "Modelling Tobacco Demand: How the Illicit Cigarette Market Constrains the Legal Market" 
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: TRUE
Entry1: "Modelling Tobacco Demand: How the Illicit Cigarette Market Constrains the Legal Market"
Entry2: "\\textbf{Cassandra Pengelly} \\vfill Thesis Draft 1" # textbf for bold
#Entry3: "Thesis draft 1"
Uni_Logo: Tex/logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry3: "Under the supervision of: \\vfill Prof. W. Boshoff"
# Entry4: "Stellenbosch University \\vfill September 2021"
#Entry6: September 2021
#Entry7: 
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
# AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
# Author1: "Nico Katzke^[__Contributions:__  \\newline _The authors would like to thank no institution for money donated to this project. Thank you sincerely._]"  # First Author - note the thanks message displayed as an italic footnote of first page.
# Ref1: "Prescient Securities, Cape Town, South Africa" # First Author's Affiliation
# Email1: "nfkatzke\\@gmail.com" # First Author's Email address
# 
# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"
# 
# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Price elasticity \\sep Tobacco control \\sep Cigarettes \\sep Illicit cigarettes \\sep Excise duties" # Use \\sep to separate 
JELCodes: "D12 \\sep H21 \\sep I18 \\sep C40" 

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.3 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: TRUE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
Example_data <- Texevier::Ex_Dat

write_rds(Example_data, path = "data/Example_data.rds")
#list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

References are to be made as follows: @fama1997[p. 33] and @grinold2000 Such authors could also be referenced in brackets [@grinold2000] and together [@fama1997 \& @grinold2000]. Source the reference code from scholar.google.com by clicking on ``cite'' below article name. Then select BibTeX at the bottom of the Cite window, and proceed to copy and paste this code into your ref.bib file, located in the directory's Tex folder. Open this file in Rstudio for ease of management, else open it in your preferred Tex environment. Add and manage your article details here for simplicity - once saved, it will self-adjust in your paper.

> I suggest renaming the top line after \@article, as done in the template ref.bib file, to something more intuitive for you to remember. Do not change the rest of the code. Also, be mindful of the fact that bib references from google scholar may at times be incorrect. Reference Latex forums for correct bibtex notation.


Section \ref{data} describes the data used. Section \ref{method} explains the vecto autoregression method used.


# Data  \label{data}

Data cleaning

```{r, echo=FALSE, include=FALSE, results='hide', eval=TRUE}
#list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

# read in the data - add the dataset's path to filePath
library(readxl)
filePath <- as.character("C:/Users/Cassandra/OneDrive/Documents/2021 Academics/Thesis/Thesis/data/Data.xlsx")
data <- read_excel(filePath)
source("code/data_clean.R")
log_data <- data_clean(data)
```


Discussion of data should be thorough with a table of statistics and ideally a figure.


The plots below (\ref{Figure1}) graph the time series for cigarette quantity, legal and illicit real prices and income. All the variables have been logged; and the x-axis shows the year.

```{r Figure1, echo=FALSE, warning =  FALSE, fig.align = 'center', fig.cap = "Time Series Plot \\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 6}

source("code/ts_plot_log.R")
Plot <- ts_plot_log(log_data)
source("code/plot_ts.R")
ts <- plot_ts(log_data)


```


```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Caption Here \\label{Figure2}", fig.height = 3, fig.width = 6, dev = 'png'}

ExampleData <- read_rds( "data/Example_data.rds")

source("code/Example_Plot_Scatter.R") # Load a function from your 'code' folder. This e.g. plots scatters to your own preferences.
source( "code/Data_Create.R") #

ExampleData <- Data_Create(N = 100) # Same as the ExampleData loaded above - this is just a function to create the stored data.

g <- Example_Plot_Scatter(DataInput = ExampleData,
                          X = "Height_Score",
                          Y = "Weight_Score",
                          Z = "Agility_Score",
                          Theme = theme_bw(), # run ?ggthemes for other themes.
                          Title = "", # I prefer to use the caption set above.
                          Ylab = "Height",
                          Xlab = "Lenght",
                          LegendTitle = "Agility",
                          TitleSize = 10,
                          LabSize = 10)

g

# Although the functions above are really simple, the principle is simple: containing calculations and data wrangling in their own functions will make this template much cleaner and more manageable.
# When you start working, delete these meaningless functions and replace with your own...

```
Figure \ref{ACF} shows the autocorrelation functions for each of the variables. The persistence is quite high for all of the 4 variables.

```{r Figure3, echo = FALSE, warning =  FALSE, fig.align = 'center', fig.cap = "Autocorrelation Function Plots \\label{ACF}", fig.height = 5, fig.width = 6, dev = 'png'}

source("code/ACF.R") 
Plot_acf <- ACF(log_data)

```

To reference the plot above, add a ``\\label'' after the caption in the chunk heading, as done above. Then reference the plot as such: As can be seen, Figures \ref{Figure1}  and \ref{Figure2} are excellent, with Figure \ref{Figure2} being particularly aesthetically pleasing due to its device setting of Tikz. The nice thing now is that it correctly numbers all your figures (and sections or tables) and will update if it moves. The links are also dynamic.

#  Methodology \label{method}

## Subsection
Ideally do not overuse subsections. It equates to bad writing.^[This is an example of a footnote by the way. Something that should also not be overused.]

## Math section

Equations should be written as such:

\begin{align}
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \label{eq1} \\
\int_{x = 1}^{\infty}x_{i} = 1 \notag
\end{align}

If you would like to see the equations as you type in Rmarkdown, use $ symbols instead (see this for yourself by adjusted the equation):

$$
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \\
\int_{x = 1}^{\infty}x_{i} = 1
$$

Note again the reference to equation \ref{eq1}. Writing nice math requires practice. Note I used a forward slashes to make a space in the equations. I can also align equations using  __\&__, and set to numbering only the first line. Now I will have to type ``begin equation'' which is a native \LaTeX command. Here follows a more complicated equation:


\begin{align}
	y_t &= c + B(L) y_{t-1} + e_t   \label{eq2}    \\ \notag
	e_t &= H_t^{1/2}  z_t ; \quad z_t \sim  N(0,I_N) \quad \& \quad H_t = D_tR_tD_t \\ \notag
		D_t^2 &= {\sigma_{1,t}, \dots, \sigma_{N,t}}   \\ \notag
		\sigma_{i,t}^2 &= \gamma_i+\kappa_{i,t}  v_{i, t-1}^2 +\eta_i  \sigma_{i, t-1}^2, \quad \forall i \\ \notag
		R_{t, i, j} &= {diag(Q_{t, i, j}}^{-1}) . Q_{t, i, j} . diag(Q_{t, i, j}^{-1})  \\ \notag
		Q_{t, i, j} &= (1-\alpha-\beta)  \bar{Q} + \alpha  z_t  z_t'  + \beta  Q_{t, i, j} \notag
\end{align}

Note that in \ref{eq2} I have aligned the equations by the equal signs. I also want only one tag, and I create spaces using ``quads''.

See if you can figure out how to do complex math using the two examples provided in \ref{eq1} and \ref{eq2}.


# Results

Tables can be included as follows. Use the _xtable_ (or kable) package for tables. Table placement = H implies Latex tries to place the table Here, and not on a new page (there are, however, very many ways to skin this cat. Luckily there are many forums online!).


```{r ShortTable, results = 'asis'}

library(xtable)
data <- mtcars[1:5,] %>% tibble::as_tibble()

table <- xtable(data, caption = "Short Table Example \\label{tab1}")
  print.xtable(table,
             # tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H',
             # scalebox = 0.3,
             comment = FALSE,
             caption.placement = 'bottom'
             )

```

To reference calculations __in text__, _do this:_ From table \ref{tab1} we see the average value of mpg is `r mean(mtcars[1:5,]$mpg)`.

Including tables that span across pages, use the following (note that I add below the table: ``continue on the next page''). This is a neat way of splitting your table across a page.

Use the following default settings to build your own possibly long tables. Note that the following will fit on one page if it can, but cleanly spreads over multiple pages:

```{r LongTable, results = 'asis'}

library(xtable)

data = mtcars %>% tibble::as_tibble()
  addtorow          <- list()
  addtorow$pos      <- list()
  addtorow$pos[[1]] <- c(0)
  addtorow$command  <- c(paste("\\hline \n",
                               "\\endhead \n",
                               "\\hline \n",
                               "{\\footnotesize Continued on next page} \n",
                               "\\endfoot \n",
                               "\\endlastfoot \n",sep=""))
table <- xtable(data, caption = "Long Table Example")
  print.xtable(table,
             tabular.environment = "longtable",
             floating = FALSE, # Leave this as is.
             table.placement = 'H', # Leave this as is.
             booktabs = T, # Aesthetics
             include.rownames = FALSE,  # Typically you don't want this in a table.
             add.to.row = addtorow, # For adding the Continued on next page part...
             comment = FALSE,
             caption.placement = 'top',  # Where do you want the caption?
             size="\\fontsize{12pt}{13pt}\\selectfont"  # Size of text in table..
             )
# See https://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf for table inspiration
```

\hfill

<!-- hfill can be used to create a space, like here between text and table. -->


## Huxtable

Huxtable is a very nice package for making working with tables between Rmarkdown and Tex easier.

This cost some adjustment to the Tex templates to make it work, but it now works nicely.

See documentation for this package [here](https://hughjonesd.github.io/huxtable/huxtable.html). A particularly nice addition of this package is for making the printing of regression results a joy (see [here](https://hughjonesd.github.io/huxtable/huxtable.html#creating-a-regression-table)). Here follows an example:


```{r, results = 'asis'}

if(!require(huxtable)) install.packages(huxtable)
library(huxtable)
data(diamonds, package = 'ggplot2')
Title <- "Regression Output"
Label <- "Reg01"
lm1 <- lm(price ~ carat, diamonds)
lm2 <- lm(price ~ depth, diamonds)
lm3 <- lm(price ~ carat + depth, diamonds)
htab <-
huxreg(lm1, lm2, lm3,
                statistics = c(N = "nobs", R2 = "r.squared"),
                note = "%stars%.") %>%
  set_caption(Title) %>%
  set_label(Label)
# More settings:
font_size(htab) <- 12
# Let's change regression names: this is slightly hacky, but works. Comment out this section to see what the default looks like:
  Names <- c( "Reg1", "Reg2", "Reg3")
  for(i in 1:length(Names)) {
    htab[1,][[1+i]] <- Names[i]
  }
# Now simply call the table:
htab

```


# Lists

To add lists, simply using the following notation

* This is really simple

    + Just note the spaces here - writing in R you have to sometimes be pedantic about spaces...

* Note that Rmarkdown notation removes the pain of defining \LaTeX environments!

# Conclusion


<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

